Project 1 for Complex Adaptive Systems

### 2018-02-20 paper.tex
Updating for Vanessa

% Figure for part 2
 \begin{figure}[H]
 \centering
    \includegraphics[width=100mm]{prettypicture}

@@

While return maps that look like figure \ref{prettypicture} seemed to occur more often, it would be interesting to look at the distributions of fitness values $r_i$ that produce the more exotic return maps.  This is outside of the scope of this paper.
\begin{figure*}[!t]
\centering
\subfloat[]{\includegraphics[width=3.5in]{Fig4a}%
\label{te}}
\hfill
\subfloat[]{\includegraphics[width=3.5in]{Fig4b}%
\label{fig_second_case}}
\caption{Simulation results for the network.}
\label{te_avg}
\end{figure*}
\subsection{Direction of Information Flow}
\noindent In order to assess that direction of information flow, from Global to Local scales and vice versa, the authors in \cite{Walker} take advantage of {\it Transfer Entropy}. Transfer Entropy is defined mathematically in \cite{Schreiber} as
$$T^{(k)}_{Y \rightarrow X} = \sum_n p(x_{n+1}, x_n^{(k)}, y_n^{(k)}) \log \left[ \frac{p(x_{n+1}|x_n^{(k)}, y_n^{(k)})}{p(x_{n+1}|x_n{(k)}}\right]$$
Where $x_n^{(k)}$ is an embedded state in the $k$-dimensional phase spate defined as $x_n^{(k)} = (x_n, \cdots, x_{n-k+1})$. \\

@@

\noindent In Figure \ref{te}, we see qualitatively similar results as to what was demonstrated in \cite{Walker}. The quantitative difference in the location and magnitude of the peaks can be attributed to either chance or estimation method. For low values of the global coupling parameter ($\epsilon$), we see information flow is stronger in the bottom-down direction (from local to global scale). As $\epsilon$ increases the direction reverses, and top-down causation begins to dominate. We note again that we are qualitatively in agreement with the previous work \cite{Walker}. There is however a subtle quantitative difference in our results. It appears from Figure \ref{te} that this reversal of causation occurs at a value of $\epsilon = 0.3$. In an effort to analyze this claim more rigorously, we repeat the entire simulation and estimation procedure $30$ times. The right panel of Figure \ref{te_avg} shows the difference $T_{M\rightarrow X} - T_{X \rightarrow M}$ as a function of $\epsilon$ for 30 different simulations. The mean is also plotted, and we can see clearly that this reversal of information flow occurs right at $\epsilon = 0.3$.

>>>>

% Figure for part 2
 \begin{figure}[t]
 \centering
    \includegraphics[width=100mm]{prettypicture}

@@

While return maps that look like figure \ref{prettypicture} seemed to occur more often, it would be interesting to look at the distributions of fitness values $r_i$ that produce the more exotic return maps.  This is outside of the scope of this paper.

\begin{figure*}[!t]
\centering
\subfloat[]{\includegraphics[width=3.5in]{Fig4a}%
\label{te}}
\hfill
\subfloat[]{\includegraphics[width=3.5in]{Fig4b}%
\label{fig_second_case}}
\caption{(a) Top-down, $T_{M\rightarrow X}$ (solid), and bottom-up, $T_{X\rightarrow M}$ (dashed), causal information transfer as a function of the global coupling parameter $\epsilon$ for coupled logistic maps. (b) The difference (Top-down minus bottom-up) in causal information transfer for $30$ coupled systems as well as the mean as a function of $\epsilon$ (dashed). Vertical line at $\epsilon = 0.3$ illustrates the directional reversal of causal information transfer.}
\label{te_avg}
\end{figure*}

\subsection{Direction of Information Flow}
\noindent In order to assess that direction of information flow, from Global to Local scales and vice versa, the authors in \cite{Walker} take advantage of {\it Transfer Entropy}. Transfer Entropy is defined mathematically in \cite{Schreiber} as
$$T^{(k)}_{Y \rightarrow X} = \sum_n p(x_{n+1}, x_n^{(k)}, y_n^{(k)}) \log \left[ \frac{p(x_{n+1}|x_n^{(k)}, y_n^{(k)})}{p(x_{n+1}|x_n{(k)}}\right]$$
Where $x_n^{(k)}$ is an embedded state in the $k$-dimensional phase spate defined as $x_n^{(k)} = (x_n, \cdots, x_{n-k+1})$. \\

@@

\noindent In Figure \ref{te}, we see qualitatively similar results as to what was demonstrated in \cite{Walker}. The quantitative difference in the location and magnitude of the peaks can be attributed to either chance or estimation method. For low values of the global coupling parameter ($\epsilon$), we see information flow is stronger in the bottom-down direction (from local to global scale). As $\epsilon$ increases the direction reverses, and top-down causation begins to dominate. We note again that we are qualitatively in agreement with the previous work \cite{Walker}. There is however a subtle quantitative difference in our results. It appears from Figure \ref{te} that this reversal of causation occurs at a value of $\epsilon = 0.3$. In an effort to analyze this claim more rigorously, we repeat the entire simulation and estimation procedure $30$ times. The right panel of Figure \ref{te_avg} shows the difference $T_{M\rightarrow X} - T_{X \rightarrow M}$ as a function of $\epsilon$ for 30 different simulations. The mean is also plotted, and we can see clearly that this reversal of information flow occurs right at $\epsilon = 0.3$. Finally, we note that this result is intuitively satisfactory since it coincides with the black stars in Figure \ref{prettypicture}, the value of $\epsilon$ for which the system is completely synchronized.

\subsection{Additional Analysis}
Here we continue our exploration of the relationship between local and global population dynamics.
